Formalization of Abstract Rewriting

### 2025-02-23 Relations/Paper/Definitions.tex
typo fix
intro done
Update after call

\section{Definitions}
\label{sec:Definitions}
The following definitions are provided to ensure clarity and precision
in our discussion. Each subsection specifies the Agda file(s) which contain formalizations of the given definitions.

\begin{definition}
    An abstract rewrite system (\emph{ARS}) is a structure $\mathcal{A} = (A, R_\alpha)$ where
     $A$ is a set of elements and $R_\alpha$ is a set of binary relations on $A$.
\end{definition}

For the rest of this section, let $A$ be a fixed set, and $R$ be a relation on $A$.

@@

\subsection{Closure operators (\texttt{ClosureOperators.agda})}
\begin{notation}
  The following notions are standard.  For precise definitions,
  see \texttt{ClosureOperators.agda}.
  \begin{enumerate}
    \item $R^r$ denotes the \emph{reflexive closure} of $R$.
    \item $R^s$ denotes the \emph{symmetric closure} of $R$.
    \item $\tclos{R}$ denotes the \emph{transitive closure} of $R$.
    \item $R^* = (R^r)\tclos{}$ denotes the \emph{reflexive-transitive closure} of $R$.
    \item $R^= = (R^s)^*$ denotes the \emph{equivalence relation generated by} $R$.
  \end{enumerate}
\end{notation}

@@

We next define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
\subsection{Normalization (\texttt{ARS-Properties.agda})}
\begin{definition} The following definitions relate to normalization. Let $A$ and $R$ be as above, and let $a \in A$.
  \begin{description}
    \item[$a \in \NF_R$] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.   
    \item[$a \in \WN_R$] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
    \item[$a \in \SN_R$] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = {(y,x) | (x,y) \in R}$. See Section \ref{sec:Well-foundedness}. 
  \end{description}
\end{definition}

\subsection{Confluence (\texttt{ARS-Properties.agda})}
\begin{definition} The following definitions relate to confluence. Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$a \in \WCR_R$] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \CR_R$] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \CRs_R$] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
        \item[$a \in \NPe_R$] \emph{$a$ has the equivalence normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
        \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$. 
        \item[$a \in \UN_R$] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
        \item[$a \in \UNto_R$] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
    \end{description}
\end{definition}

For each of the subsets defined above we denote in bold face the proposition that the subset contains all of $A$.
That is, for $\mathrm{X} \in \{\WCR , \CR , \NP , \UN \}$ we write $\mathbf{X}$ for the statement that $x \in \mathrm{X}_R$ for all $x \in A$.

In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote normal form.

@@

\begin{notation}
    $R \models \mathbf{X}$ is $\forall a.\; a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $R \models \gNP$, etc. 
\end{notation}

\begin{definition} \hfill
    \begin{description}
        \item[$R \models \gInc$] \emph{$R$ is increasing} if there exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $a, b \in A$,
        $Rab \to |a| < |b|$  
    \end{description}
\end{definition}

Having a size function that maps to the natural numbers is computationally taxing to satisfy. 
Further, it takes us outside of purely relational theory. The following definitions are for properties which allow us to forgo $\gInc$, for further discussion see Subsection \ref{subsec:def}.
\begin{definition} \label{def:rp} Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description} 
        \item[$s : \nat \to A$] \emph{A sequence $s \in A$} is a function from the natural numbers to $A$.  
        \item[$s \in R-increasing$] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
        \item[$a$ is an $s$-bound] if $s (i) \mstep a$ for all $i \in \nat$. 
        \item[$a \in \BP_R$] if for all $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound.  
        \item[$R \models \gRPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
        \item[$R \models \gRP$] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
        $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$. See Definition \ref{def:mf}. 
    \end{description}
\end{definition}

@@

The following is immediate.
\begin{proposition}\hfill 
    \begin{enumerate}
        \item $\gInc \implies \gRPm$
        \item $\gRPm \implies \gRP$
    \end{enumerate}
\end{proposition}

@@

We wanted to generalize $\RP$ and thought that with $\RPm$ we had a good candidate for a weaker definition that 
did not rely on the notion of $\MF$. We show that this weaker definition is 
in fact an equivalent definition in the following proof in \texttt{ARS-Implications.agda}:

@@

\begin{definition} Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there is finitely many $b \in A$ such that $a \rstep b$.  
    \end{description}
\end{definition}

>>>>

\section{Definitions}
\label{sec:Definitions}
The following definitions are provided to ensure clarity and precision
in our discussion. Each subsection specifies the Agda file(s) which contains formalizations of the given definitions.

\begin{definition}
    An abstract rewrite system (\emph{ARS}) is a structure $\mathcal{A} = (A, R_\alpha)$ where
     $A$ is a set and $R_\alpha$ is a set of binary relations on $A$.
\end{definition}

For the rest of this paper, let $A$ be a fixed set, $R$ be a relation on $A$, and $a \in A$.

@@

\subsection{Closure operators (\texttt{ClosureOperators.agda})}

\begin{notation} 
The following notations are standard.
  \begin{enumerate}
    \item $R^r$ denotes the \emph{reflexive closure} of $R$.
    \item $R^s$ denotes the \emph{symmetric closure} of $R$.
    \item $\tclos{R}$ denotes the \emph{transitive closure} of $R$.
    \item $R^* = (R^r)\tclos{}$ denotes the \emph{reflexive-transitive closure} of $R$.
    \item $R^= = (R^s)^*$ denotes the \emph{equivalence relation generated by} $R$.
  \end{enumerate}
\end{notation}

@@

We next define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
\subsection{Normalization (\texttt{ARS-Properties.agda})}
\begin{definition} The following definitions relate to normalization. 
  \begin{description}
    \item[\ule{$\mathbf{a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
    \item[\ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
    \item[\ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$ 
    (see Section \ref{sec:Well-foundedness} for the notion of accessibility).
  \end{description}
\end{definition}

\subsection{Confluence (\texttt{ARS-Properties.agda})}
\begin{definition} The following definitions relate to confluence.
    \begin{description}
        \item[$a \in \WCR_R$] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \CR_R$] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \CRs_R$] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
        \item[$a \in \NPe_R$] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
        \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
        \item[$a \in \UN_R$] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
        \item[$a \in \UNto_R$] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
    \end{description}
\end{definition}

\begin{notation}
    For each of the subsets $\mathrm{X}$ defined above we write 
    $R \models \mathbf{X}$ if $\forall a.\; a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $R \models \gNP$, etc.
    That is, for $\mathrm{X} \in \{\WCR , \CR , \NP , \UN, \dots \}$ we write $\mathbf{X}$ for the statement that $x \in \mathrm{X}_R$ for all $x \in A$.
\end{notation}

In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote the set of normal forms.

@@

\begin{definition} \hfill
    \begin{description}
        \item[\ule{$R \models \gInc$}] \emph{$R$ is increasing} if there exists a ``size function'' $|{-}| : A \to \nat$ satisfying, for all $a, b \in A$,
        $(a \rstep b) \implies |a| < |b|$
    \end{description}
\end{definition}

Having a size function that maps to the natural numbers can be computationally taxing to satisfy.
Further, it takes us outside of purely relational theory. The following definitions are for properties which allow us to forgo $\gInc$, for further discussion see Subsection \ref{subsec:def}.
\begin{definition} \label{def:rp} \hfill
    \begin{description}
        \item[\ule{$s : \nat \to A$}] \emph{A sequence $s \in A$} is a function from the natural numbers to $A$.
        \item[\ule{$s$ is $R$-increasing}] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
        \item[\ule{$a$ is an $s$-bound}] if $s (i) \mstep a$ for all $i \in \nat$.
        \item[\ule{$a \in \BP_R$}] \emph{$a$ has the bound property} if for each $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound.
        \item[\ule{$R \models \gRP$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
        $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$. 
        \item[\ule{$R \models \gRPm$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
    \end{description}
\end{definition}

@@

The following is immediate.
\begin{proposition}\hfill
    \begin{enumerate}
        \item $\gInc \implies \gRP$
        \item $\gRP \implies \gRPm$
    \end{enumerate}
\end{proposition}

@@

We wanted to generalize $\RP$ and thought that with $\RPm$ we had a good candidate.
 We show that this weaker definition is
in fact equivalent in the following proof in \texttt{ARS-Implications.agda}:

@@

\begin{definition} \hfill
    \begin{description}
        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
    \end{description}
\end{definition}

### 2025-02-23 Relations/Paper/Formalization.tex
Update after call

The following is a summary of the differences in definition we have used as mentioned in Section \ref{sec:Definitions}. 
\begin{itemize}
    \item $\SN$ : We make use of the well-founded definition, rather than the finite reduction sequence definition.
    \item $\NPe$ : We use the equivalent $\NP$ definition. 
    \item $\Inc$ : We use the more general property $\RP$.      
\end{itemize}

As mentioned, the $\Inc$ property imposes a computationally demanding requirement. However, $\Inc$ is used only in Theorem 1.2.3 
and the only crucial aspect of $\Inc$ needed for the proof is that no $R$-increasing 
sequence can have an upper bound.
We establish that the properties $\RP$ and $\RPm$ were sufficient for replacing $\Inc$ in the theorem (see Subsection \ref{subsec:theorems}), 
which led us to examine the condition in $\RP$ more closely. This condition provides a generalization of the notion of a normal form, 
which we explore in detail in Section \ref{sec:Implications}.

@@

\subsection{Theorems}\label{subsec:theorems}
\subsubsection{Newman's Lemma}
There are three proofs of Newman's Lemma ($\SN \land \WCR \implies \CR$) given in \terese. 
The first and third of these proofs make use of classical assumptions. The second proof is amenable to a 
constructive formalization as shown in the following function in \texttt{ARS-NewmansLemma.agda}:

@@

We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using $\MF$. 
The formalizations of the remaining theorems are all found in \texttt{ARS-Theorems.agda}. 
\subsubsection{Theorem 1.2.2}
There are three parts to this theorem. 
\begin{description}
    \item[($i$)] $\gCR \implies \gNPe \implies \gUN$
    \item[($ii$)] $\gWN \land \gUN \implies \gCR$  
    \item[($iii$)] $\gCRs \implies \gCR$
\end{description}

($i$) is formalized in:
\begin{itemize}
    \item \verb|CR→NP : R isCR → R isNP₌|
    \item \verb|NP→UN : R isNP₌ → R isUN|
    \item \verb|CP→UN : R isCR → R isUN|
\end{itemize}

($ii$) is formalized in:
\begin{itemize}
    \item \verb|ii : R isWN × R isUN → R isCR|
\end{itemize}
Note that we have provided a proof with the weaker hypothesis of $\gUNto$.

@@

\subsubsection{Theorem 1.2.3}
The following definition is required for this theorem.
\begin{definition} Let $a \in A$.
    \begin{description}
        \item[$a \in CP_R$] \emph{$a$ has the cofinality property} if there exists a 
        (not necessarily strictly) increasing sequence starting from $a$ such that every
        reduct of $a$ reduces to some element of the sequence.
    \end{description}
\end{definition}

@@

In $\mathtt{i\to}$ we again provide a generalization by using $\gUNto$ rather than $\gUN$.

A formalization of ($ii$) is provided in: 
\begin{itemize}
    \item \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|
\end{itemize}
This is a fundamentally classical result, and so the result is only classically equivalent to $\gSN$.

@@

The reverse implication of ($iv$) is formalized in: 
\begin{itemize}
    \item \verb|iv : R isCP → R isCR|
\end{itemize}
We did not formalize $\gCR \to \gCP$ as it requires the ARS to be countable.

>>>>

The following is a summary of the differences in definition we have used as mentioned in Section \ref{sec:Definitions}. 
\begin{itemize}
    \item $\SN$ : We define this via the notion of accessibility rather than the non-existence of infinite reduction sequences. 
     See Section \ref{sec:Well-foundedness} for further discussion.
    \item $\NPe$ : We use the equivalent $\NP$ definition. 
    \item $\Inc$ : We use the more general property $\RP$.      
\end{itemize}

As mentioned, the $\Inc$ property can impose a computationally demanding requirement. However, $\Inc$ is used only in Theorem 1.2.3 
and the only crucial aspect of $\Inc$ needed for the proof is that no $R$-increasing 
sequence can have an upper bound.
We establish that the equivalent properties $\RP$ and $\RPm$ are sufficient for replacing $\Inc$ in the theorem (see Subsection \ref{subsec:theorems}), 
which led us to examine the condition on $s (i)$ appearing inside $\RP$ more closely. This condition provides a generalization of the notion of a normal form, 
which we explore in detail in Section \ref{sec:Implications}.

@@

\subsection{Theorems}\label{subsec:theorems}
\subsubsection{Newman's Lemma}
There are three proofs of Newman's Lemma ($\SN \land \WCR \implies \CR$) given in \terese. 
The first and third of these proofs make use of classical reasoning. The second proof is amenable to a 
constructive formalization as shown in the following function in \texttt{ARS-NewmansLemma.agda}:

@@

We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using a condition distilled from $\RP$. 
The formalizations of the remaining theorems are all found in \texttt{ARS-Theorems.agda}. 
\subsubsection{Theorem 1.2.2}
There are three parts to this theorem. 
\begin{description}
    \item[($i$)] $\gCR \implies \gNPe \implies \gUN$
    \item[($ii$)] $\gWN \land \gUN \implies \gCR$  
    \item[($iii$)] $\gCRs \implies \gCR$
\end{description}

($i$) is formalized in:
\begin{itemize}
    \item \verb|CR→NP : R isCR → R isNP₌|
    \item \verb|NP→UN : R isNP₌ → R isUN|
\end{itemize}

($ii$) is formalized also from the weaker hypothesis of $\gUNto$:
\begin{itemize}
    \item \verb|ii : R isWN × R isUN → R isCR|
    \item \verb|UN→∧WN→CR : R isUN→ → R isWN → R isCR|
\end{itemize}

@@

\subsubsection{Theorem 1.2.3}
The following definition is required for this theorem.
\begin{definition}\hfill
    \begin{description}
        \item[$a \in CP_R$] \emph{$a$ has the cofinality property} if there exists a 
        (not necessarily strictly) increasing sequence starting from $a$ such that every
        reduct of $a$ reduces to some element of the sequence.
    \end{description}
\end{definition}

@@

In $\mathtt{i\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.

A formalization of ($ii$) is provided in: 
\begin{itemize}
    \item \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|
\end{itemize}
This is an inherently classical result, and so the result is only classically equivalent to $\gSN$.

@@

The reverse implication of ($iv$) is formalized in: 
\begin{itemize}
    \item \verb|iv : R isCP → R isCR|
\end{itemize}
We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions.

% the ARS to be countable.

### 2025-02-23 Relations/Paper/Implications.tex
Update after call

\begin{definition}\label{def:mf}  Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$a \in \MF_R$] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
        \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
        \item[$a \in \SMseq_R$] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists 
        an $i \in \nat$ such that $s (i) \in \MF$. 
        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is also strongly minimalizing.
        \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.

@@

@@

Trivially, the following also holds. 
\begin{proposition}\label{prop:nftomf}
    $\NF \implies \MF$ 
\end{proposition}    
\begin{proof}
    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
\end{proof}

With these minimal definitions we can see the taxonomy of concepts that relate to termination and confluence.

@@

The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. The classical property of being minimally decidable is 
required to complete the implication from $\SN$ to $\WN$, as can be seen in our formalization

@@

Similarly, the property of being minimally decidable is required in order to show that $\SM$ implies $\WM$.

We are interested in seeing which combination of properties a relation requires in order to be complete (that is, $\gCR$ and $\gSN$). 
The following tables show either that a given combination is complete, or the appropriate counterexample which demonstrates why 
those properties do not provide a property higher on the taxonomical hierarchy.

The first table explores where the properties hold locally, the second explores where the properties hold globally. Counterexamples in the 
first table assume $\WCR$ and in the second table assume $\gWCR$.

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begin{table}[h!]
    \centering
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
        \hline
        \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
        \hline
        $\UNto$ &  CE-\ref{CE:4}, CE-\ref{CE:12}     & CE-\ref{CE:4}, CE-\ref{CE:7}       & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$\footnotemark[1] , CE-\ref{CE:4}            & $\CR$\footnotemark[1] , $\SN$ \\
        \hline
        $\NP$ & CE-\ref{CE:10},CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1]  , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
        \hline
        $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
        \hline
        $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
        \hline

@@

\begin{remark} The following are the key takeaways from the implication tables. \hfill
    \begin{enumerate}
        \item The property $\gWCR$ can sometimes be a substitute for the classical 
        property required for $\SN \implies \WN$ (and similarly $\SM \implies WM$).   
        \item $\gWN \land \gUNto \implies \gCR$ doesn't require any classical assumptions
         or $\gWCR$ for the implication to $\gCR$, unlike $\gSN \land \gUNto$. 
        \item $\gWN \land \gUNto \implies \gCR$ only holds when the properties are global. The 
        counterexample provided illustrates why $\WCR \land \WN \land \UNto \nRightarrow \CR$.
        \item Both $\SM$ and $\WN$ are required for $\SN$, this connection is explored in Subsection \ref{subsec:SMWNSN}.
        \item We have a generalization of Newman's Lemma as $\SM \land \gWCR \implies \CR$. This is explored in Subsection \ref{subsec:newnewman}.
    \end{enumerate}
\end{remark}

\subsubsection{Generalized Newman's Lemma}\label{subsec:newnewman}
One interesting outcome from investigating the normalization taxonomy was a generalization of Newman's Lemma.

@@

This proof follows the same steps as the second proof of Newman's Lemma found in \terese, but 
uses the generalization $\SM$ of $\SN$.

>>>>

\begin{definition}\label{def:mf} \hfill
    \begin{description}
        \item[$a \in \MF_R$] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
        \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
        \item[$a \in \SMseq_R$] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists 
        an $i \in \nat$ such that $s (i) \in \MF$. 
        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This 
        definition is to be understood inductively).
        \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.

@@

Trivially, the following holds. 
\begin{proposition}\label{prop:nftomf}
    $\NF \implies \MF$ 
\end{proposition}    
\begin{proof}
    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
\end{proof}

@@

Proposition \ref{prop:nftomf} suggests that we consider $\MF$ as a termination property in its own right. This leads us to 
explore the following broader taxonomy of concepts relating to termination and confluence.

@@

The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. The classical property of being minimally decidable is 
required to complete the implication from $\SN$ to $\WN$, as can be seen in our formalization \sacomment{Rewrite this section}

@@

The same property is similarly required in order to show that $\SM$ implies $\WM$.

We are interested in seeing which combination of properties a relation requires in order to be complete (that is, $\gCR$ and $\gSN$). 
The following tables show either that a given combination is complete, or the appropriate counterexample which demonstrates why 
those properties do not provide the next property on the hierarchy.

The first table explores where the properties hold locally, the second explores where the properties hold globally. Counterexamples in the 
first table assume $\WCR$ and in the second table assume $\gWCR$.
\clearpage
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begin{table}[h!]
    \centering
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
        \hline
        \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
        \hline
        $\UNto$ &  CE-\ref{CE:4}, CE-\ref{CE:12}     & CE-\ref{CE:4}, CE-\ref{CE:7}       & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$\footnotemark[1] , CE-\ref{CE:4}            & $\CR$\footnotemark[1] , $\SN$ \\
        \hline
        $\NP$ & CE-\ref{CE:10},CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1]  , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
        \hline
        $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
        \hline
        $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
        \hline

@@

\begin{remark} The following are the key takeaways from the implication tables. \hfill
    \begin{enumerate}
        \item The property $\gWCR$ can sometimes be a substitute for the classical 
        property required for $\SN \implies \WN$ (and similarly $\SM \implies \WM$).   
        \item $\gWN \land \gUNto \implies \gCR$ does not require any classical assumptions
         or $\gWCR$ for the implication to $\gCR$, unlike $\gSN \land \gUNto$. 
        \item $\gWN \land \gUNto \implies \gCR$ only holds when the properties are global. The 
        counterexample provided illustrates why $\WCR \land \WN \land \UNto \nRightarrow \CR$.
        \item We have a generalization of Newman's Lemma as $\SM \land \gWCR \implies \CR$. This is explored in Subsection \ref{subsec:newnewman}.
        \item Both $\SM$ and $\WN$ are required for $\SN$, this connection is explored in Subsection \ref{subsec:SMWNSN}.
    \end{enumerate}
\end{remark}

\subsection{Generalized Newman's Lemma}\label{subsec:newnewman}
One interesting outcome from investigating the normalization taxonomy was a generalization of Newman's Lemma.

@@

This proof follows the same steps as the second proof of Newman's Lemma found in \terese, but 
uses the weaker assumption $\SM$ in place of $\SN$.
